\chapter{How to Use the utdiss2 Package}
\index{How to Use the utdiss2 Package%
@\emph{How to Use the utdiss2 Package}}%

\section{Preamble}
\index{Preamble@\emph{Preamble}}%

The preamble of the document starts like this:
\begin{verbatim}
     \documentclass[12pt]{report}
     \usepackage{utdiss2}
\end{verbatim}
\index{commands!documentclass@\cn{documentclass}}%
\index{commands!usepackage@\cn{usepackage}}%

The first line declares ``\texttt{report}'' as the document 
class, 
\index{document class}%
with an option of 12pt for the character size, 
which is slightly greater that usual (the default is 10pt), but is
what the Office of the Graduate School (OGS) recommends.
You may include other options, as in any other \LaTeX{} document.

The second line loads the \texttt{utdiss2} package, 
\index{utdiss2 package@{\texttt{utdiss2} package}}%
which contains a set of commands intended to produce a document fulfilling
the official requirements for a doctoral dissertation or master's thesis or
report. Besides that, you may include other packages. 
For instance:
\begin{verbatim}
     \usepackage{amsmath,amsthm,amsfonts,amscd}
\end{verbatim}
for mathematical symbols, or,
\begin{verbatim}
     \usepackage{draftcopy}
\end{verbatim}
to have a large ``watermark'' across each page of your document that
says, ``DRAFT.''


The next few commands in the preamble are required.

\cn{author\{Craig William McCluskey\}}
\index{commands!author@\cn{author}}%
Replace my name in the command by your
full, official University name.  Make it combination of lower and uppercases.

\cn{address\{9905 Chukar Circle\bslash\bslash\ Austin, Texas 78758\}}
\index{commands!address@\cn{address}}%
Replace my address with your *permanent* (not local) address. Use
\texttt{\bslash\bslash} to separate address lines.

\cn{title\{Writing a Doctoral Dissertation with \cn{LaTeX\{\}} at
the University of Texas at Austin\} }
\index{commands!title@\cn{title}}%
Replace the name of this document
in this command by your dissertation title. If the title consists of more
than one line, it should be in inverted pyramid form. You may have to specify
the line breakings by \texttt{\bslash\bslash} commands.

\cn{supervisor[Isaac Newton]\{Johannes Kepler\} }
\index{commands!supervisor@\cn{supervisor}}%
This document has two supervisors listed. See the source file
(disstemplate.tex) for information on how to have only one supervisor.
This command can be broken across lines as it is in the source file and
as the \cn{committeemembers} command is shown below.

\begin{verbatim}
\committeemembers
        [Erwin Schr\"odinger]
        [Albert Einstein]
        [Charles Townes]
        {Arthur Schawlow}
\end{verbatim}
\index{commands!committeemembers@\cn{committeemembers}}%
This document shows four non-supervisor committee members. See the source
file (disstemplate.tex) for information on how to have a different number.

\cn{previousdegrees\{B.S.\} } Replace B.S. with your previous degree.

The next few commands in the preamble are optional.
\begin{verbatim}
%\graduationmonth{...}
%\graduationyear{...}
%\typist{...}
\end{verbatim}
Their use is documented in the source file.

At this point, if you are writing a master thesis or report
you must use the optional \cn{degree} and \cn{degreeabbr} commands
and specify
\index{master}
\index{master!master thesis}
\index{commands!masterthesis@\cn{masterthesis}}
\index{master!master report}
\index{commands!masterreport@\cn{masterreport}}
\begin{verbatim}
%\degree{MASTER OF ARTS}
%\degreeabbr{M.A.}
%\masterreport
%\masterthesis
\end{verbatim}
as documented in the source file. By default the document is formated
as a \emph{dissertation}%
\footnote{The command \cn{dissertation} is also provided for symmetry.}%
\index{commands!dissertation@\cn{dissertation}}


The default spacing for both text and quoted text is doublespaced.
That can be changed with the following self-explanatory commands: 
\begin{verbatim}
\oneandonehalfspacing 
\singlespacing
\oneandonehalfspacequote
\singlespacequote
\end{verbatim}
\index{commands!oneandonehalfspacing@\cn{oneandonehalfspacing}}%
\index{commands!singlespacing@\cn{singlespacing}}%
\index{commands!oneandonehalfspacequote@\cn{oneandonehalfspacequote}}%
\index{commands!singlespacequote@\cn{singlespacequote}}%

Some versions of LaTeX in combination with some types of printers
produce printed output that has incorrect vertical margins.
The command \cn{topmargin 0.125} is provided to allow easy adjustment
if it's needed.

If there are 10 or more sections, 10 or more subsections for a section,
etc., you need to make an adjustment to the Table of Contents with the
command \cn{longtocentry}.
\index{commands!longtocentry@\cn{longtocentry}}%
This command allocates the proper horizontal space for double-digit
numbers.


\section{Document}
\index{Document@\emph{Document}}%

Next comes the actual text. It could be a sequence of chapters divided
into sections, subsections, etc., all in the main file:
\begin{verbatim}
\chapter{...}     % The first chapter. The
                  % \chapter command is of the form
                  % \chapter[..]{..} or \chapter{..} where
    ... text ...  % [...] is the entry in table of contents
                  % and {...} is the chapter heading printed
                  % in the body of the document.
\section{...}     %
                  % IMPORTANT: If your chapter heading consists
                  % of more than one line, it will be auto-
    ... text ...  % matically broken into separate lines.
                  % If you don't like the way LaTeX breaks the
                  % chapter heading into lines, however, use
\section{...}     % `\newheadline' command to break lines.
                  % NEVER USE \\ IN SECTIONAL (E.G., CHAPTER,
    ... text ...  % SECTION, SUBSECTION, SUBSUBSECTION) HEADINGS!
                  %
\chapter{...}     % This is Chapter 2.
    ... text ...
\section{...}
    ... text...
\subsection{...}
    ... more text ...
\subsubsection{...}
    ... more text ...
\appendix         % The appendix begins here.
% \appendices     % If more than one appendix chapters,
                  % use \appendices instead of \appendix
\chapter{...}     % First appendix chapter, i.e., Appendix A.
\section{...}     % This is appendix section A.1.
    .................
\end{verbatim}
\index{commands!chapter@\cn{chapter}}%
\index{commands!section@\cn{section}}%
\index{commands!subsection@\cn{subsection}}%
\index{commands!appendix@\cn{appendix}}%
\index{commands!appendices@\cn{appendices}}%

Or, the chapters can be written in different files like this document
and be loaded by \cn{include} commands:
\begin{verbatim}
\include{chapter-introduction}
\include{chapter-instructions}
\include{chapter-howtouse}
\include{chapter-makingbib}
\include{chapter-tables+figs}
\include{chapter-math}
\appendices
\index{Appendices@\emph{Appendices}}%
\include{chapter-appendix1}
\include{chapter-appendix2}
\include{chapter-appendix3}
\end{verbatim}
\index{commands!include@\cn{include}}%
Having the chapters in separate files makes the main .tex file simpler
and allows chapters to be easily re-ordered (just swap the order of the
include commands) or left (commented) out for draft copies.

Note: If you have only one appendix, in addition to using
\cn{appendix} instead of \cn{appendices}, you must leave out the
\cn{chapter} definition at the start of the appendix's text. Putting
it in will cause the insertion of an extra page with only the word
Appendix on it and will cause the appendix to be labeled Appendix 1,
both of which are poor form if there is only one appendix.

If you are writing a short dissertation 
\index{short dissertation}%
that does not require 
chapters, you need to use the command \cn{nochapters} 
\index{commands!nochapters@\cn{nochapters}}%
just before the first section:

\begin{verbatim}
\nochapters 

\section{...}     % First section.
    ... text ... 
\section{...}     % Second section.
    ... text ... 
        (...)
\end{verbatim}

Next comes the bibliography.
\index{bibliography}%
It can be made by hand like this:
\begin{verbatim}
\begin{thebibliography}{foo}
\bibitem ...   
\end{thebibliography}
\end{verbatim}
\index{commands!environments!thebibliography}%
Or it can also be generated with BiB\TeX{}, 
\index{BiBTeX@BiB\TeX{}}%
as explained in chapter \ref{c:bib}.

Finally the vita is produced like this:
\begin{verbatim}
\begin{vita}
     % Insert your brief biographical sketch here. 
     % Your permanent address and the name of the 
     % typist(s) are generated automatically.
\end{vita}

\end{verbatim}
